Decompositions of relative Chevalley groups

### 2015-10-08 congrsubgr-boundgen.tex

\begin{proof}[Proof of \cref{thm:width}] The first statement of the theorem is contained in \cref{lemma:srRI1_width}.
The second and third statement follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}

>>>>

\begin{proof}[Proof of \cref{thm:width}] The second assertion of the theorem is contained in \cref{lemma:srRI1_width}.
The the first and the third assertions follow from \cref{lemma:Z1p,lemma:width-dedekind}. \end{proof}

### 2015-10-08 paper.tex

Applying \cref{thm:DennisVaserstein} and generalizing (in the special case $\Phi=\rD_\ell$) Nikolov's \cite[Proposition~1]{NikProdDecomp} to arbitrary rings we obtain the following result.
\begin{thm}\label{thm:spin-sln-prod}
Assume that $\sr(I) \leqslant 2$ then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of (regularly embedded) subgroups of type $\rA_{\ell-1}$.
\end{thm}

>>>>

Applying \cref{thm:DennisVaserstein} and generalizing (in the special case $\Phi=\rD_\ell$) Nikolov's \cite[Proposition~1]{NikProdDecomp} to arbitrary rings we obtain the following result.
\begin{thm}\label{thm:spin-sln-prod}
Assume that $\sr(I) \leqslant 2$. Then the group $\Epin_{2\ell}(R, I)=\E(\rD_\ell, R, I)$ is a product of at most $9$ conjugates of (regularly embedded) subgroups of type $\rA_{\ell-1}$.
\end{thm}
